Boundary Labeling for annotated documents

### 2018-01-25 LaTeX/Paper.tex
Paper: Finished initial re-write of Section 2.2. Program: No changes.

In our Algorithm we first create the routing graph that will be used from here onward. To achieve this, we ge through the annotated text word by word, and measure the length $le(w_i)$ of each word $w_i \in l_j$ that is not part of an annotation to determine its placement in the text. Afterwards, we create new vertices above and below the whitespace characters $h_k, h_{k+1}$ preceding and succeeding $w_i$. These vertices are located in the space $S(l_{j-1},l_j), S(l_j,l_{j+1})$ between the word's line and its surrounding lines $l_{j-1}$ and $l_{j+1}$, as described in the previous section. Whenever an annotation is encountered, a single vertex is added above the last non-annotation word in $S(l_{j-1},l_j)$ at $pos(h_k)+le(w_i)/2$.
For a representation of this process in pseudocode, see Alg.~\ref{alg:GraphCreation}.
%To create leaders that exclusively use the space not taken up by a word's bounding rectangle, we decided to use a graph similar to the one Loose \cite{Loose2015} used.
%As each vertex represents a physical location, they will have co-ordinates associated with them, and the vertices representing the sites will hold additional information regarding its leader and label. 
%The graph is constructed by placing vertices between the lines, located next to each corner of a word's bounding rectangle, with two consecutive words in a line sharing the two vertices associated with their adjacent corners. 
%For the sites, we inserted an additional vertex above the center of the word, which will serve as the leader's starting point. After placing all vertices, we created edges between each vertex and the closest horizontal neighbour to both sides, and between nodes that are located exactly above or below each other, and exactly one line apart. (For a representation in Pseudocode, see Alg.~\ref{alg:GraphCreation})

For the routing part of the algorithm, we work through the annotations $a \in A$ in the order they appear in the text, placing each as far up as possible, skipping any annotation that cannot be placed above its leader's source node. We will also use fixed ports located in the top left corner of each label. This allows us to place annotations by only knowing their port location, which can be inferred from their leader's ending point. The routing area between the text and label areas will be used to bridge the gap between the highest reachable point within the routing graph and the highest possible label placement by connecting the two via an OPO-leader.%Kann man das so sagen?

%TODO: Expand/rework this!
The algorithm's input consists of the Graph $G$ and a set of sites $V_{ann} \subset V$ which will be routed using a depth-first search algorithm, restricted to only selecting vertices located above or to the right of the current vertex $v_{curr}$, prioritizing moving up whenever possible.  After the algorithm terminates, it returns a set with routing information for each vertex, which contains a Path $P=\{v_1, \cdots, v_n\}$, leading from the site to the text area's border, along with information on how to draw the OPO-Segment that connects to the Label's port. If the routing for any given site failed, the path consists of a single vertex - the site. (For an illustration in Pseudocode see Alg.~\ref{alg:DFS}.)

>>>>

First, we create the graph that will be used for the routing part of the algorithm. To achieve this, we go through the annotated text word by word in reading order, and measure the length $le(w_i)$ of each word $w_i$ that is not part of an annotation to determine its placement in the text.  At this point, we can also assign a line $l_j$ to it. Afterwards, we create new vertices above and below the whitespace characters $h_k, h_{k+1}$ preceding and succeeding $w_i$. These vertices are located in the space $S(l_{j-1},l_j), S(l_j,l_{j+1})$ between the word's line and its surrounding lines $l_{j-1}$ and $l_{j+1}$, as described in the previous section. Whenever an annotation is encountered, a single vertex is added above the last non-annotation word in $S(l_{j-1},l_j)$ at $pos(h_k)+le(w_i)/2$.
For a representation of this process in pseudocode, see Alg.~\ref{alg:GraphCreation}.
%To create leaders that exclusively use the space not taken up by a word's bounding rectangle, we decided to use a graph similar to the one Loose \cite{Loose2015} used.
%As each vertex represents a physical location, they will have co-ordinates associated with them, and the vertices representing the sites will hold additional information regarding its leader and label. 
%The graph is constructed by placing vertices between the lines, located next to each corner of a word's bounding rectangle, with two consecutive words in a line sharing the two vertices associated with their adjacent corners. 
%For the sites, we inserted an additional vertex above the center of the word, which will serve as the leader's starting point. After placing all vertices, we created edges between each vertex and the closest horizontal neighbour to both sides, and between nodes that are located exactly above or below each other, and exactly one line apart. (For a representation in Pseudocode, see Alg.~\ref{alg:GraphCreation})

For the routing part of the algorithm, we work through the annotations $a \in A$ in the order they appear in the text, placing each as far up as possible, skipping any annotation that cannot be placed above its leader's source node. We will also use fixed ports located in the top left corner of each label. %This allows us to place annotations by only knowing their port location, which can be inferred from their leader's ending point.
The routing area, which is located between the text and label areas, will be used to bridge the gap between the highest reachable point within the routing graph and the highest possible label placement by connecting the two via an OPO-leader.%Kann man das so sagen?

The routing algorithm itself uses only the Graph $G$ and the set of sites $V_{ann} \subset V$ which will be routed using a depth-first search algorithm, restricted to only selecting vertices located above or to the right of the current vertex $v_{curr}$, prioritizing moving up whenever possible. It will terminate upon reaching the right text border or if all possible paths failed to reach the text border. At this point, it will return a set with routing information for each vertex, which contains a Path $P=\{v_1, \cdots, v_n\}$, leading from the site to the text area's border, along with information on how to draw the OPO-Segment that connects to the Label's port. If the routing for any given site failed, the path consists of a single vertex - the site. (For an illustration in Pseudocode see Alg.~\ref{alg:DFS}.)
